メタ分析

### 2021-04-14 how-to-meta1.Rmd
update meta analysis
update

---
title: "メタ分析：メタ分析の実施手順"
---

@@

<iframe src="https://docs.google.com/presentation/d/e/2PACX-1vRD1R5yRiru8JJbm6TCvSZr16jOA01I0mZHd86v7CFDKrQ7ltoENxuik5MJ9Mz1Q7b4_AJ_E8TciptA/embed?start=false&loop=false&delayms=30000" frameborder="0" width="480" height="389" allowfullscreen="true" mozallowfullscreen="true" webkitallowfullscreen="true"></iframe>

>>>>

---
title: "メタ分析"
---

@@

```{r echo=FALSE}
library(zousan)
embed_slide("https://ykunisato.github.io/ccp-lab-slide/spring_seminar_JSSP_2021/meta_analysis/slide.html#1")
```
